Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-06-20 ms.tex
adding results when using PCA on each amplifier separately

\begin{deluxetable*}{ccc}[b!]
\tablecaption{Summary of Noise Sources in Weak Lens +8 Aperture Dark Test}\label{tab:noiseSummaryWLP8}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Noise Description} &
\colhead{$\sigma$} &
\colhead{$\sigma$} \\
\colhead{} &
\colhead{DN} &
\colhead{ppm}\\
}
\startdata
Ideal Photon Noise & 4,400 & 113 \\
Ideal Uncorrelated Read Noise & 1,300 & 33 \\
\hline
Measured Read Noise (no correction) & 23,500 & 600 \\
Measured Read Noise (reference pixel correction) & 10,800 & 280 \\
Measured Read Noise (reference channel subtraction) & 9,700 & 250 \\
Measured Read Noise (row-by-row median subtraction) & 6,000 & 150 \\
Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 \\
Measured Read Noise (smoothed 161 px kernel interpolating over aperture) & 3,300 & 85 \\
Measured Read Noise (smoothed 40 px kernel on top of aperture) & 900 & 23 \\
\enddata
\tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 Time Series.
The ppm units are assuming a 60\% well depth or 3.9$\times 10^7$ DN during an integration.
The noise is the sum within a 70 pixel radius source aperture and 75 to 100 pixel background aperture (in DN) or relative to the photon signal (in ppm).
The integration is assumed to be a bright source with 2 groups of 1 integration each up the ramp (Correlated Double Sampling or CDS mode).}
\end{deluxetable*}

@@

\subsubsection{Reference Channel Subtraction}
We note that the 4 channels can sometimes exhibit the same 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by unilluminated channels.
We attempt to subtract an amplifier 0's time series from all amplifiers.
Of course, this means that this amplifier is perfectly subtracted and no noise or signal remains in this 1/4 of the image.
The subtraction step should increase the read noise on an individual pixel by $\sim \sqrt{2}$ because the errors from the subtracted pixel should add in quadrature to the original pixels.
This increase in read noise on a per-pixel level might be acceptable if it decreases the correlated errors along the rows.
On the other hand, if the each amplifier exhibits its own individual correlated noise behavior, the reference amplifier will fail to subtract out all correlated noise and may introduce more noise.

@@

>>>>

\begin{deluxetable*}{ccc}[b!]
\tablecaption{Summary of Noise Sources in Weak Lens +8 Aperture Dark Test}\label{tab:noiseSummaryWLP8}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Noise Description} &
\colhead{$\sigma$} &
\colhead{$\sigma$} \\
\colhead{} &
\colhead{DN} &
\colhead{ppm}\\
}
\startdata
Ideal Photon Noise & 4,400 & 113 \\
Ideal Uncorrelated Read Noise & 1,300 & 33 \\
\hline
Measured Read Noise (no correction) & 23,500 & 600 \\
Measured Read Noise (reference pixel correction) & 10,800 & 280 \\
Measured Read Noise (reference channel subtraction) & 9,700 & 250 \\
Measured Read Noise (row-by-row median subtraction) & 6,000 & 150 \\
Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 \\
Measured Read Noise (5 Component PCA on each amplifier) & 3,300 & 140 \\
Measured Read Noise (smoothed 161 px kernel interpolating over aperture) & 3,300 & 85 \\
Measured Read Noise (smoothed 40 px kernel on top of aperture) & 900 & 23 \\
\enddata
\tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 Time Series.
The ppm units are assuming a 60\% well depth or 3.9$\times 10^7$ DN during an integration.
The noise is the sum within a 70 pixel radius source aperture and 75 to 100 pixel background aperture (in DN) or relative to the photon signal (in ppm).
The integration is assumed to be a bright source with 2 groups of 1 integration each up the ramp (Correlated Double Sampling or CDS mode).}
\end{deluxetable*}

@@

\subsubsection{Reference Channel Subtraction}
We note that the 4 channels can sometimes exhibit the same 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by un-illuminated channels.
We attempt to subtract an amplifier 0's time series from all amplifiers.
Of course, this means that this amplifier is perfectly subtracted and no noise or signal remains in this 1/4 of the image.
The subtraction step should increase the read noise on an individual pixel by $\sim \sqrt{2}$ because the errors from the subtracted pixel should add in quadrature to the original pixels.
This increase in read noise on a per-pixel level might be acceptable if it decreases the correlated errors along the rows.
On the other hand, if the each amplifier exhibits its own individual correlated noise behavior, the reference amplifier will fail to subtract out all correlated noise and may introduce more noise.

@@

If we treat each amplifier separately, the PCA model is more effective in reducing 1/f noise.
We begin by keeping 5 principal components within each amplifier and subtracting these from each amplifier separately.
The resulting standard deviation of the time series is 2900 to 3870 DN.
